### 2019-05-24 sections/intuition.tex
explain synchronous events
Removed all mention of clearing editors

Input events drive evaluation of tasks.
When the system receives a valid event, it applies this event to the current task, which results in a new task.
In this way the system communicates with the environment.
Inputs are synchronous.
We assume systems react instantaneously to each of those events.

In \TOPHAT, \emph{editors} are the basic method of communication with the environment.
Editors are modelled after input widgets from graphical user interfaces.
There are different editors, denoted by different box symbols.
Take for example an editor holding the integer seven: $\Edit 7$.
Such an editor reacts to two kinds of events.
The first are change events, for example the values $42$ or $37$, which are of the same type.
The second is a clear event $\Empty$, which empties the editor.
This results is an empty editor $\Enter \Int$, annotated to only hold integers.

@@

Another observation is the set of input events a task can react to.
% This is important for generating user interfaces.
For example, the task $\Edit 7$ can react to value events and empty events, as discussed before.

>>>>

Input events drive evaluation of tasks.
When the system receives a valid event, it applies this event to the current task, which results in a new task.
In this way the system communicates with the environment.
Inputs are synchronous, which means the order of execution is completely determined by the order of the inputs.

In \TOPHAT, \emph{editors} are the basic method of communication with the environment.
Editors are modelled after input widgets from graphical user interfaces.
There are different editors, denoted by different box symbols.
Take for example an editor holding the integer seven: $\Edit 7$.
Such an editor reacts to change events, for example the values $42$ or $37$, which are of the same type.

@@

Another observation is the set of input events a task can react to.
% This is important for generating user interfaces.
For example, the task $\Edit 7$ can react to value events, as discussed before.
